\section{Past Efforts at Image Reconstruction in Intensity Interferometry}
\iffalse
Several theoretical and computational approaches for phase reconstruction with II have been proposed. \cite{gamo1963triple} introduced the concept of triple-intensity correlation, which \cite{goldberger1963use} subsequently applied in an experiment to observe scattered particles in microscopic systems. Sato conducted experiments to measure the diameter and phase of asymmetrical objects, suggesting that triple correlation could extend II to image stellar bodies \citep{sato1978imaging, sato1979computer, sato1981adaptive}. However, achieving a satisfactory signal-to-noise ratio (SNR) remained a significant challenge for this approach.

\cite{GerchbergSaxton1972} suggested an iterative method to determine the phase from the image and diffraction plane pictures. This method relies on accurate initial estimates and is vulnerable to slow convergence otherwise. \cite{Fienup1982} introduced a Hybrid Input-Output algorithm that incorporates feedback mechanisms to improve convergence rate and robustness, particularly in noisy environments.

Later, \cite{holmes2010two} proposed an alternative method that utilizes the Cauchy-Riemann relations to reconstruct 1-D images. They also extended the approach to 2-D images across a range of signal-to-noise (SNR) values. This algorithm was applied to simulated data of stellar objects using II, considering both existing and forthcoming Imaging Cherenkov Telescope Arrays (IACTs) with a large number of telescopes \citep{nunez2010stellar, nunez2012high, nunez2012imaging}. However, this method faces challenges related to computational complexity when attempting to generalize to higher dimensions.

\cite{Li2014} suggested a flexible iterative Regularization method that incorporates prior information (e.g., sparsity, smoothness, or non-negativity) to reduce the ill-posedness of the phase retrieval problem. This method is more robust against noise and stabilizes the solution against artefacts and spurious solutions. Nevertheless, it faces challenges regarding the choice of the regularization parameter, computational complexity, and sensitivity to the initial guess.

The Transport-of-Intensity Equation (TIE) method is a non-interferometric technique first proposed by \cite{Teague1983} that relates the intensity variations along the optical axis to the phase of the optical fields. This method enables phase retrieval from intensity measurements taken at multiple planes. \cite{Zhang2020} proposed a method to obtain a \textquotedblleft universal solution\textquotedblright\ to the TIE by employing a \textquotedblleft maximum intensity assumption\textquotedblright, thereby converting the TIE into a Poisson equation which is then solved iteratively. More recently, \cite{Kirisits2024} have explored hybrid methods that combine the TIE with other equations, such as the Transport of Phase Equation (TPE). These approaches leverage the strengths of both equations to improve phase retrieval accuracy. This method is universally applicable, as it works for arbitrarily shaped apertures, handles non-uniform illumination, and accommodates inhomogeneous boundary conditions. It guarantees convergence, although the speed of convergence depends on the quality of the initial guess, and the final results are influenced by the boundary conditions.

%%%**************************8

%\documentclass{article}
%\usepackage{amsmath}
%\begin{document}
\fi
Several approaches have been developed for phase reconstruction in intensity interferometry (II). \cite{gamo1963triple} introduced triple-intensity correlation, applied by \cite{goldberger1963use} to microscopic systems and extended by \cite{sato1978imaging, sato1979computer, sato1981adaptive} to measure stellar diameters and phases, though limited by low signal-to-noise ratio (SNR). \cite{GerchbergSaxton1972} proposed an iterative phase retrieval method using image and diffraction plane data, sensitive to initial estimates and convergence speed. \cite{Fienup1982} improved this with the Hybrid Input-Output algorithm, enhancing robustness in noisy conditions. \cite{holmes2010two} utilized Cauchy-Riemann relations for 1-D and 2-D image reconstruction, applied to simulated stellar data with Imaging Cherenkov Telescope Arrays \citep{nunez2010stellar, nunez2012high, nunez2012imaging}, but faced computational complexity for higher dimensions. \cite{Li2014} introduced a regularized iterative method incorporating priors (e.g., sparsity) to mitigate noise and ill-posedness, though challenged by parameter tuning and initial guess sensitivity. The Transport-of-Intensity Equation (TIE), proposed by \cite{Teague1983}, retrieves phase from intensity variations across planes; \cite{Zhang2020} solved TIE as a Poisson equation using a maximum intensity assumption, while \cite{Kirisits2024} combined TIE with the Transport of Phase Equation for improved accuracy across arbitrary apertures and non-uniform illumination, with convergence dependent on initial guesses and boundary conditions.

%\end{document}
%%%**************

With non-linearity built into their architecture, artificial neural networks (ANNs) empowered by deep learning methods are promising for exploring the task of reconstructing images of stellar objects from ground-based observations. Convolutional Neural Networks (CNNs), with their specialized architecture for processing two-dimensional datasets, are a natural choice for image processing tasks. In astronomical image reconstruction projects, a common challenge is that the interferometric data are typically undersampled as well as noisy.  Therefore, the CNN architectures and deep learning methods employed must be capable of reliably learning both the global context of the training dataset and the local features within it. Among the various CNN architectures, U-Net models \citep{ronneberger2015u} have proven successful in such tasks.

Furthermore, given that achieving a high signal-to-noise ratio (SNR) is often challenging in astronomical datasets, it is immensely beneficial if additional data can be generated using the available information from the observed sky density distribution and ground-based observations (II data, in our case) of the sources under investigation. Generative Adversarial Networks (GANs), introduced by \cite{goodfellow2014generative}, have been successful in such data augmentation tasks. Conditional GAN (cGAN) architectures, proposed by \cite{mirza2014conditional} and applied to a wide variety of datasets by \cite{isola2017image}, leverage additional information about the images in the training datasets and have demonstrated remarkable robustness in image recovery across diverse data types.

In the astrophysical context, \cite{schawinski2017galaxypics} employed a GAN model to recover features — such as spiral arms, central bulges, and disk structures of galaxies — from noise-affected images. \cite{mustafa2019cosmogan} developed and customized a Deep Convolutional GAN, dubbed \textquotedblleft CosmoGAN\textquotedblright, capable of generating high-fidelity weak-lensing convergence maps of dark matter distribution that statistically reproduce real weak lensing structures. \cite{coccomini2021lightweightgan} have successfully generated credible images of planets, nebulae, and galaxies using \textquotedblleft lightweight\textquotedblright\ and \textquotedblleft physics-uninformed\textquotedblright\ GANs to produce synthetic images of celestial bodies. They also generated a \textquotedblleft Hubble Deep Field-inspired\textquotedblright\ wide-view simulation of the universe. 

Let us now discuss the details of our procedure and method.