\section{Introduction}
Humans instinctively feel a symbiotic relationship with the stars. One of the primary scientific projects of humanity is to figure out what the stars are and how do they do what they do. The first obvious step in this project, beyond measuring their global parameters like diameter, mass, orbital and astrometric elements, is to obtain images of the stars with all details of the stellar surfaces. In case of the Sun, this is done routinely by observatories and Sun-observation satellites. But such a routine still remains a challenge even for the $\alpha$-Centauri system, our nearest stellar neighbour. The objective is to achieve capability of high fidelity image reconstruction of distant stars. Two interferometry based techniques, namely, Michelson Interferometry (MI) and Intensity Interferometry (II) have emerged during the last century to address this objective. A discussion of the development of these two approaches and comparison of their respective merits and challenges can be found in \citep{Rai2025}. The work reported here presents the results of a first effort at applying a Conditional Generative Adversarial (neural) Network (cGAN) to image reconstruction of a fast rotator using its simulated II observations.  

The foundational basis of II stems from the pioneering experiments and theoretical investigations carried out initially by Hanbury Brown and Twiss (HBT) \citep{HBT56Lab,brown1957interferometry, brown1958interferometry} and, later, by \cite{glauber1963quantum} and others. The correlation between photons \textcolor{magenta}{emitted by a thermal source within a certain bandwidth}(known as ``photon bunching'', also widely referred to as the \textquotedblleft HBT effect\textquotedblright) measured by a pair of photon detectors in two partially coherent beams of light was reported in 1956 by \cite{HBT56Lab}. \cite{Rai2025} present a recent variant of this experiment, carried out with pseudo-thermal light. The HBT Effect and the related theoretical investigations laid the foundation for the modern field of Quantum Optics.

Hanbury Brown and his collaborators led the creation and installation of the historic II facility at Narrabri, Australia, and reported the measurement of angular diameters of 32 stars and a few multiple star-systems \citep{hanbury1974angular}. Soon after this work, however, II observations of stars was stalled for over four decades due to the limits of the then available photon detectors and data processing equipment. With gradual mitigation of such issues, proposals to utilize Imaging Atmospheric Cherenkov Telescope (IACT) facilities for conducting II observations of stars have emerged\citep{LeBohec2006, nunez2010stellar, nunez2012high, 2013APh....43..331D} as a secondary science application of these facilities during moonlit nights. SII observations at VERITAS, MAGIC, and H.E.S.S. are now being reported \citep[e.g.,][]{2024ApJ...966...28A,2024MNRAS.529.4387A,2025MNRAS.537.2334V}. This approach has the potential to enhance the scientific output of existing IACT facilities and the upcoming ones such as the Cherenkov Telescope Array Observatory (CTAO). Simulations \citep[e.g.,]{10.1093/mnras/stab2391, 10.1093/mnras/stac2433} have shown that recent advancements in photon detectors hold promising prospects of high-precision stellar parameter measurements by such facilities.

The thrust of such efforts has been to measure average and global parameters  such as angular diameters, binary separations, and orbital characteristics of stars and star systems. High-fidelity imagery, however, would transcend such integrated view of the systems and offer direct insights into dynamic stellar surface phenomena, including limb darkening, convection cells, granulation, star spots, oblateness and gravity darkening in rapid rotators and atmospheric structures, akin to the detailed observations routinely conducted on our own Sun.

As it stands today, studies grappling with various issues of image reconstruction are being reported \citep{Haubois2009, Norris2021AZCyg, Liu2024SuperresolutionII, Liu2025}. Projects of MI-based image reconstruction have made substantial progress as demonstrated in the cases of Betelgeuse \citep{Haubois2009} and AZ~Cyg \citep{Norris2021AZCyg}. On the other hand, II-based methods are at a nascent stage. Recently Liu et al. have demonstrated \citep{Liu2024SuperresolutionII, Liu2025} through outdoor experiments using ``active optical intensity interferometry'', imaging of millimeter-scale targets located at km scale distances and achieving resolution ~14 times better than a single telescope’s diffraction limit. A \textquotedblleft flexible computational algorithm\textquotedblright reconstructs images from intensity correlations, overcoming atmospheric turbulence and optical imperfections.

We report here, the results of our attempt -- the first of its kind -- to construct the gravity-darkened sky-images of fast rotating stars consistent with their respective simulated ground-based II-observations using a cGAN neural network architecture. Image reconstruction of gravity-darkened fast-rotating stars has long been examined using various methods in MI \citep{vanBelle2001, DomicianodeSouza2003, DomicianodeSouza2005, mcalister2005first, Monnier2007, Pedretti2009, Zhao2009, Martinez2021}. Recently photosphere oblateness of $\gamma$-Cassiopeia \citep{Archer-arXiv-2025} has been measured at the VERITAS observatory using II. These results put our work in context, and our work presented here is a natural next step especially of the work by \cite{Archer-arXiv-2025}. We implement a cGAN model \citep{isola2017image} to reconstruct images of fast-rotating stars using their simulated Intensity Interferograms and sky-intensity distributions as input data for training, testing, and validation. The intensity interferograms are synthetically generated by simulations of the fast rotators using two hypothetical IACT facilities having, respectively, arrays of six and of nine Cherenkov telescopes. The images predicted by the trained cGAN shows promising results in reconstructing the stars' shapes and sizes. The reconstructed brightness distributions are then assessed using moments.

This paper is organized as follows. The next section discusses briefly the past efforts at image reconstruction using II, followed by a section that discusses the signal and noise characteristics in II observations \sout{incorporating the effects of Earth's rotation using IACT arrays with a focus on the fast rotating stars}\textcolor{magenta}{of fast rotating stars (FRSs). An outline of the method to incorporate the effect of Earth's rotation during the observation is also presented}. The following section introduces the cGAN formulation and its structure. The fifth section details the parameter selection for training the network for the task of image reconstruction. The sixth section presents the results of the trained network both visually and via image moments. Finally, the paper concludes with a discussion of the overall results.

